Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-14 paper/ms.tex
update manuscript

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights incompleteness in the membership
  selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Planet radius versus age, for the known transiting planets.} 
    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
    were queried from the NASA Exoplanet Archive on 13 July 2020.
    Precise ages are known for only a small fraction of the gray points.
		\label{fig:rpvsage}
	}
\end{figure}

@@

If the RM measurements prove that the validated planet is real, a
campaign to measure the mass timed to coincide with TESS sectors 36
and 37 ({\it i.e.}, from late March to late May of 2021) would
significantly ease the extraction of the planetary Doppler signal.
The reason is that the radial velocities, activity indicators, and
photometry could then be modeled simultaneously, which would greatly
constrain a Gaussian process model for the spot-induced RV signal.

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.65\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights incompleteness in the membership
  selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Planet radii versus ages, for the known transiting planets.} 
    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
    are from the NASA Exoplanet Archive on 13 July 2020.
    Precise ages are known for only a small fraction of the gray points.
		\label{fig:rpvsage}
	}
	\vspace{-0.5cm}
\end{figure}

@@

If the RM measurements prove that the validated planet is real, a
campaign to measure the mass timed to coincide with TESS sectors 36
and 37 (late March to late May of 2021) would
significantly ease the extraction of the planetary Doppler signal.
The reason is that the RVs, activity indicators, and photometry could
be modeled simultaneously. This would greatly constrain models of
the spot-induced RV signal.  The mass measurement would likely be
worthwhile in order to improve understanding of the planet's
contraction and photoevaporation history.

While we hope that RV observations will be pursued, data acquired
during the first TESS mission extension may also help in
understanding the system
\citep{bouma_extend_2017,huang_expected_2018}.  Any misalignment
between the star's spin axis and the planet's orbit should induce
nodal precession, which could yield large changes in the transit
duration given the system's high impact parameter.
If observed, this could be a spectroscopy-free method for 
confirming the planet
